### 2010-03-15 papers/icfp-2010-desc/paper_desc.tex
Desc@ICFP: math code for All and all predicate.

Then, we have to translate the notion of algebra in our dependent
setting. This is achieved by the predicate $\All{D}{X}{P}{x}$ that,
intuitively, states that $\Bhab{P}{X \To \Set}$ holds everywhere in
$x$. Based on that knowledge, we ought to be able to prove that $P$
holds for $\Con{xs}$. We close our elimination principle by taking an
argument $x$ in $\Mu{D}$ and claiming that the motive $P$ is realised
on $x$.

@@

@@

\note{Shall we give the code of $\All$?}

>>>>

Then, we have to translate the notion of algebra in our dependent
setting. This is achieved by the predicate $\All{D}{X}{P}{x}$
(Fig.\ref{fig:all-predicates}) that, intuitively, states that
$\Bhab{P}{X \To \Set}$ holds everywhere in $x$. Based on that
knowledge, we ought to be able to prove that $P$ holds for
$\Con{xs}$. We close our elimination principle by taking an argument
$x$ in $\Mu{D}$ and claiming that the motive $P$ is realised on $x$.

@@

\[
\begin{array}{ll}
%%
\stk{
\begin{array}{@{}ll}
\All{}{}{}{} : & \PITEL{\V{D}}{\Desc}
                 \PITEL{\V{X}}{\Set}
                 \PITEL{\V{P}}{\V{X} \To \Set} \\
               & \PI{\V{xs}}{\descop{D}{\Mu{X}}} 
                 \Set 
\end{array} \\
\All{\DId}{X}{P}{x} \mapsto P\: x \\
\All{(\DConst{Z})}{X}{P}{x} \mapsto Z \\
\All{(\DProd{D}{D'})}{X}{P}{\pair{d}{d'}{}} \mapsto \TIMES{\All{D}{X}{P}{d}}{\All{D'}{X}{P}{d'}} \\
\All{(\DSigma{S}{T})}{X}{P}{\pair{a}{b}{}} \mapsto \All{(T\: a)}{X}{P}{b} \\
\All{(\DPi{S}{T})}{X}{P}{f} \mapsto \PI{\V{s}}{S} \All{(T\: a)}{X}{P}{(f\: s)}
}
&
%%
\stk{
\begin{array}{@{}ll}
\all{}{}{}{}{} : & \PITEL{\V{D}}{\Desc}
                   \PITEL{\V{X}}{\Set}
                   \PITEL{\V{P}}{\V{X} \To \Set} \\
                 & \PITEL{\V{R}}{\PI{\V{x}}{X} P\: x}
                   \PI{\V{xs}}{\descop{D}{\Mu{X}}} 
                   \All{D}{X}{P}{xs} 
\end{array} \\
\all{\DId}{X}{P}{R}{x} = R x \\
\all{(\DConst{Z})}{X}{P}{R}{x} = z \\
\all{(\DProd{D}{D'})}{X}{P}{R}{\pair{d}{d'}{}} = \pair{\all{D}{X}{P}{R}{d}}{\all{D'}{X}{P}{R}{d'}}{} \\
\all{(\DSigma{S}{T})}{X}{P}{R}{\pair{a}{b}{}} = \all{(T\: a)}{X}{P}{R}{b} \\
\all{(\DPi{S}{T})}{X}{P}{R}{f} = \LAM{s} \all{(T\: s)}{X}{P}{R}{(f\: s)}
\end{array}
}
\]

\caption{Induction predicates}
\label{fig:all-predicates}

@@
